An Integration of Multiple Constraints in ACG

### 2013-07-16 lenls/abstract.tex
First draft of a Conclusion

>>>>

\section{Conclusion}

We have considered the problem of building a wide-coverage ACG, specifically
the problem of expressing a multitude of linguistic constraints. We have
examined previous techniques and found no satisfying solution. We have thus
provided an extension of the ACG formalism to solve the problem and justified
the need for the increased expressivity.
